Plots for Latent Hawkes Paper

### 2021-08-18 output_scripts/Paper_Plots.Rmd
current updates

# don't write to this path
data_path <- "../output/revisions/lapl_check/prior_check/"

@@

sims <- 1:50
sims <- sims[c(-37,-45,-46, -50)]

@@

```{r construct data for plot, results='hide',message=FALSE,cache=TRUE}
library(PlayerRatings)

@@

print(fit_dsnl_active, pars = c("x"))
sim_dsnl_active <- rstan::extract(fit_dsnl_active)

## social dsnl
fit_dsnl_inactive <- stan("../lib/dsnl_poisson.stan",
  data = list(
    day = 21,
    Gt = social_state_day,
    c = 1,
    sigma = 1
  ),
  iter = 1000, chains = 4, control = list(adapt_delta = 0.99)
)
print(fit_dsnl_inactive, pars = c("x"))
sim_dsnl_inactive <- rstan::extract(fit_dsnl_inactive)

>>>>

# don't write to this path
data_path <- "../output/revisions/aug_run/"

@@

## change this to just list all files with a pattern
sims <- 1:50
sims <- sims[c(-37,-45,-46, -50)]

@@

```{r construct data for plot, results='hide',message=FALSE}
library(PlayerRatings)

@@

# 
# print(fit_dsnl_active, pars = c("x"))
# sim_dsnl_active <- rstan::extract(fit_dsnl_active)

## social dsnl
fit_dsnl_inactive <- dsnl_poisson$sample(
  data = list(
    day = 21,
    Gt = social_state_day,
    c = 1,
    sigma = 1
  ),
  iter = 1000, chains = 4, control = list(adapt_delta = 0.99)
)
# print(fit_dsnl_inactive, pars = c("x"))
sim_dsnl_inactive <- rstan::extract(fit_dsnl_inactive)
